Species richness destabilizes trophic communities in freshwater ecosystems

### 2020-03-11 manuscript/bef_stability/manuscript.Rmd
Fix Latex compilation problem

$$
\begin{align}

\log_{10}S_i &= \beta_0 + \beta_R\log_{10}x_{Ri} + \epsilon_{ij}\\

S_i &= 10^{\beta_0 + \beta_R\log_{10}x_{Ri} + \epsilon_{ij}}\\

S_i &= 10^{\beta_0} \times 10^{\beta_R\log_{10}x_{Ri}} \times
10^{\epsilon_{ij}}\\

S_i &= 10^{\beta_{0}} \times x_{Ri}10^{\beta_{R}} \times 10^{\epsilon_{ij}}

\end{align}
$$

@@

\overline{CV_{sp}} ($r_\delta = `r cv_sp_on_stab`$) decreased biomass stability more than
synchrony ($r_\delta = `r sync_on_stab`$, Figure \@ref(fig:sem-plot)). Species richness had a strong
positive effect on \overline{CV_{sp}} and a strong negative effect on synchrony
whereas average trophic level and connectance had no significant effects on either
\overline{CV_{sp}} nor synchrony. The avg river size had a small positive direct
effect on synchrony ($r_\delta = `r RC1_on_sync`$). The other environmental variables had
no significant direct effects on either \overline{CV_{sp}} nor synchrony.

Indirectly through synchrony and \overline{CV_{sp}}, species richness had a total negative
effect on biomass stability ($r_\delta = `r rich_on_stab`$). Avg river size and avg
temperature had also a total effect which was negative on biomass stability
(resp. $r_\delta = `r env_on_stab["log_RC1"]`$ and $r_\delta = `r env_on_stab["log_RC2"]`$),
going through richness (resp. $r_\delta = `r env_on_richness["log_RC1"]`$ and
$r_\delta = `r env_on_richness["log_RC2"]`$).

@@

For the first time, we assessed the determinants of total biomass and temporal
biomass stability in empirical trophic communities at such high temporal and
spatial scales. We showed that species richness increased total biomass but 
decreased biomass stability. In particular, species richness decreased
synchrony and increased species CV ($\LaTeX$). Surprisingly, the avg trophic
level and connectance had no effects on either synchrony nor species CV.
Finally, we showed that high trophic group was more stable than low trophic
group but that high trophic group was responsible for the negative
stability-diversity relationship.

@@

Species richness decreased synchrony and increased \overline{CV_{sp}}. Species
richness can reduce synchrony through decrease of population size, thus raising
the role of demographic stochasticity [@loreau_species_2008] but also in the
case where species have different responses to environmental variation
[@loreau_species_2008]. While the effect of species richness on synchrony is
well understood, its effect on \overline{CV_{sp}} is more complex. Indeed, studies reported positive [@tilman_biodiversity_2006, ], neutral  [@jiang_different_2009, @olivier_independent_nodate] or negative relationships [@franssen_annual_2011, @olivier_independent_nodate]. Positive relationship between

In turn, we found that synchrony and \overline{CV_{sp}} both decreased biomass
stability, as predicted by the formulation of stability based on the CV
[@thibaut_understanding_2013].
However, it was unexpected that the average population \overline{CV_{sp}} had
a stronger negative effect on biomass stability than synchrony
[@bluthgen_land_2016; @olivier_independent_nodate]. We can advance two
hypothesis that can raise this effect. First, the opportunity for diet
differentiation can be low in streams compare to other organisms. Bird species
are for example quite specialized in seed, flying or soil arthropods or mammals
which gives opportunities for independent dynamics. Plants also can achieve
independent dynamics either spatial segregation or niche differentiation. Because
fish species even piscivorous one are quite opportunistic in their foraging.
Secondly, in trophic communities, species directly affect each other through
feeding interactions, and so could raise synchrony between species
[@raimondo_interspecific_2004] more than in systems where interactions happen
more in the form of competitive exploitation.

>>>>

$$\begin{aligned}
\log_{10}S_i &= \beta_0 + \beta_R\log_{10}x_{Ri} + \epsilon_{ij}\\
S_i &= 10^{\beta_0 + \beta_R\log_{10}x_{Ri} + \epsilon_{ij}}\\
S_i &= 10^{\beta_0} \times 10^{\beta_R\log_{10}x_{Ri}} \times10^{\epsilon_{ij}}\\
S_i &= 10^{\beta_{0}} \times x_{Ri}10^{\beta_{R}} \times 10^{\epsilon_{ij}}
\end{aligned}$$

@@

$\overline{CV_{sp}}$ ($r_\delta = `r cv_sp_on_stab`$) decreased biomass stability more than
synchrony ($r_\delta = `r sync_on_stab`$, Figure \@ref(fig:sem-plot)). Species richness had a strong
positive effect on $\overline{CV_{sp}}$ and a strong negative effect on synchrony
whereas average trophic level and connectance had no significant effects on either
$\overline{CV_{sp}}$ nor synchrony. The avg river size had a small positive direct
effect on synchrony ($r_\delta = `r RC1_on_sync`$). The other environmental variables had
no significant direct effects on either $\overline{CV_{sp}}$ nor synchrony.

Indirectly through synchrony and $\overline{CV_{sp}}$, species richness had a total negative
effect on biomass stability ($r_\delta = `r rich_on_stab`$). Avg river size and avg
temperature had also a total effect which was negative on biomass stability
(resp. $r_\delta = `r env_on_stab["log_RC1"]`$ and $r_\delta = `r env_on_stab["log_RC2"]`$),
going through richness (resp. $r_\delta = `r env_on_richness["log_RC1"]`$ and
$r_\delta = `r env_on_richness["log_RC2"]`$).

@@

For the first time, we assessed the determinants of total biomass and temporal
biomass stability in empirical trophic communities at such high temporal and
spatial scales. We showed that species richness increased total biomass but 
decreased biomass stability. In particular, species richness decreased
synchrony and increased species CV (\LaTeX). Surprisingly, the avg trophic
level and connectance had no effects on either synchrony nor species CV.
Finally, we showed that high trophic group was more stable than low trophic
group but that high trophic group was responsible for the negative
stability-diversity relationship.

@@

Species richness decreased synchrony and increased $\overline{CV_{sp}}$. Species
richness can reduce synchrony through decrease of population size, thus raising
the role of demographic stochasticity [@loreau_species_2008] but also in the
case where species have different responses to environmental variation
[@loreau_species_2008]. While the effect of species richness on synchrony is
well understood, its effect on $\overline{CV_{sp}}$ is more complex. Indeed, studies reported positive [@tilman_biodiversity_2006, ], neutral  [@jiang_different_2009, @olivier_independent_nodate] or negative relationships [@franssen_annual_2011, @olivier_independent_nodate]. Positive relationship between

In turn, we found that synchrony and $\overline{CV_{sp}}$ both decreased biomass
stability, as predicted by the formulation of stability based on the CV
[@thibaut_understanding_2013].
However, it was unexpected that the average population $\overline{CV_{sp}}$ had
a stronger negative effect on biomass stability than synchrony
[@bluthgen_land_2016; @olivier_independent_nodate]. We can advance two
hypothesis that can raise this effect. First, the opportunity for diet
differentiation can be low in streams compare to other organisms. Bird species
are for example quite specialized in seed, flying or soil arthropods or mammals
which gives opportunities for independent dynamics. Plants also can achieve
independent dynamics either spatial segregation or niche differentiation. Because
fish species even piscivorous one are quite opportunistic in their foraging.
Secondly, in trophic communities, species directly affect each other through
feeding interactions, and so could raise synchrony between species
[@raimondo_interspecific_2004] more than in systems where interactions happen
more in the form of competitive exploitation.
